Modeling Galaxy Spectral Energy Distributions in the SDSS Spectroscopic Survey

### 2002-01-31 docs/paper/paper.tex
running
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@10 75dff457-8751-0410-ab1a-cd701654ce6b

The resulting four templates are shown in Figure \ref{templates} in
the range $2000<\lambda<12000$\AA, the region which is constrained by
our observations. Figure \ref{coeffs} is a more illuminating
figure. It shows the pairwise joint distributions of $a_1/a_0$,
$a_2/a_0$, and $a_3/a_0$ in the top three panels. In the bottom panel,
three spectra taken from a one-dimensional sequence along the galay
locus are shown, showing that the spectra become progressively bluer
along that sequence.

>>>>

%The resulting four templates are shown in Figure \ref{k_espec_plot} in
%the range $2000<\lambda<12000$\AA, the region which is constrained by
%our observations. 
The top two panels of Figure \ref{k_coeffdist_plot} show the pairwise
joint distributions of $a_1/a_0$, $a_2/a_0$, and $a_3/a_0$. In the
bottom panel, three spectra taken from a one-dimensional sequence
along the galay locus are shown, showing that the spectra become
progressively bluer along that sequence. Note that constraints on the
SED become poor at the bluest and reddest edges of this diagram (the
peak of the $z$-band response is at 8700\AA). Therefore, the odd
behavior near the edges (particularly at the red edge) should not be
taken too seriously.
